---
output: github_document
always_allow_html: yes
editor_options:
  markdown:
    wrap: sentence
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# otelsdk

> OpenTelemetry SDK for R packages and projects

<!-- badges: start -->
![lifecycle](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg)
[![R-CMD-check](https://github.com/r-lib/otelsdk/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/otelsdk/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/otelsdk/graph/badge.svg?token=GAqo3S38e7)](https://app.codecov.io/gh/r-lib/otelsdk)
<!-- badges: end -->

```{r child = system.file(package = "otel", "dox", "intro.Rmd")}
```

To learn how to instrument your R code, see [Getting Started](`r gslink`)
in the otel package.

```{r}
#| include: FALSE
ctlink <- if (Sys.getenv("IN_PKGDOWN") == "true") {
  "reference/collecting.html"
} else {
  "https://otelsdk.r-lib.org/reference/collecting.html"
}
```

To learn how to collect telemetry data from an instrumented R package or
project, see [Collecting Telemetry Data](`r ctlink`).

For project status, installation instructions and more, read on.

```{r child = system.file(package = "otel", "dox", "features.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "packages.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "reference-docs.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "status.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "version-support.Rmd")}
```


## Installation

You can install the development version of otel from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("r-lib/otelsdk")
```

### Compiling from source

To compile otelsdk from source, you need to install the protobuf
library first:

* On Windows install the correct version of [Rtools](
  https://cran.r-project.org/bin/windows/Rtools/).
* On Linux install the appropriate package from your distribution.
* On macOS, you can use CRAN's [protobuf build](
  https://mac.r-project.org/bin/) or Homebrew. If you are using
  CRAN's build, then you must uninstall or unlink Homebrew protobuf:
  ```
  brew unlink protobuf
  ```

```{r child = system.file(package = "otel", "dox", "repositories.Rmd")}
```

## License

MIT © Posit, PBC
